experDesign: helping performing experiments on batches

### 2021-04-15 paper.Rmd
More tweaks

```{r osat}
library("OSAT")
gs <- setup.sample(survey, optimal = VoI)
gc <- setup.container(IlluminaBeadChip96Plate, n_batch, batch = 'plates')
gSetup <- create.optimized.setup(sample = gs, container = gc, nSim = iterations)
```

@@

```{r anticlust}
library("anticlust")
anticlust_index <- anticlustering(
  survey[, VoI],
  K = n_batch,
  objective = "variance",
  method = "exchange",
  repetitions = iterations
)
```

@@

>>>>

```{r osat}
library("OSAT")
gs <- setup.sample(survey, optimal = VoI)
gc <- setup.container(IlluminaBeadChip96Plate, n = n_batch, batch = 'plates')
gSetup <- create.optimized.setup(sample = gs, container = gc, nSim = iterations)
```

@@

```{r anticlust}
library("anticlust")
anticlust_index <- anticlustering(
  survey[, VoI],
  K = n_batch,
  objective = "variance",
  method = "exchange",
  repetitions = iterations
)
anticlust_index <- anticlustering(
  survey[, "Age"],
  K = n_batch,
  objective = "variance",
  method = "exchange",
  repetitions = iterations
)
```

@@

## Summary

Last we can compare some of the solutions

```{r compare}
OSAT_index <- get.experiment.setup(gSetup)$plates
table(batch_names(experDesign_index), anticlust_index)
# OSAT omits one sample
table(batch_names(experDesign_index)[-137], OSAT_index$plates)
table(anticlust_index[-137], OSAT_index$plates)
```
